### 2023-01-06 source/paper/main.tex
#16 Fair sentencing control experiment
#16 Continue new DD and DDD analysis

@@

\import{../../output/tables/}{britton_table2_DiD.tex}

\import{../../output/tables/}{britton_table3_DiD.tex}

\import{../../output/tables/}{fair_sentencing_DiD_t1.tex}

\import{../../output/tables/}{fair_sentencing_DiD_t2.tex}

>>>>

\begin{center}
  \includegraphics[width=.4\textwidth]{faminc_byrace_1986.png}
  \includegraphics[width=.4\textwidth]{faminc_bysex_1986.png}
  \includegraphics[width=.4\textwidth]{faminc_byrace_2010.png}
  \includegraphics[width=.4\textwidth]{faminc_bysex_2010.png}
  \end{center}

@@

\import{../../output/tables/}{britton_table2_DiD.tex}
\import{../../output/tables/}{britton_table2_DiD_control_experiment.tex}

\import{../../output/tables/}{britton_table3_DiD.tex}
\import{../../output/tables/}{britton_table3_DiD_control_experiment.tex}

\import{../../output/tables/}{fair_sentencing_DiD_t1.tex}
\import{../../output/tables/}{fair_sentencing_DiD_t1_control_experiment.tex}

\import{../../output/tables/}{fair_sentencing_DiD_t2.tex}
\import{../../output/tables/}{fair_sentencing_DiD_t2_control_experiment.tex}

\import{../../output/tables/}{DiD_1986_high_low.tex}
